\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-09 stlc-linkTran-typing.tex
Working on LT example
Working on LT example Next step is to beautify it.
Working on LT example.

\begin{table}[]
  \begin{tabular}{|l|l|l|l|l|l|l|}
  \hline
   &
    $i$ &
    $A_i$ &
    $A_i'$ &
    $\sigma_i = \LSigAdd{\sigma_{i-1}}{s_i}{A_i}$ &
    $\sigma_i' = \LSigAdd{\sigma_{i-1}'}{s_i}{A_i}$ &
    $\goodInh{..}{i_i}{\sigma_i}{\sigma_i'}$ \\ \hline
  Family STLC\_bool &
    0 &
     &
     &
    $\{\}$ &
    $\{\}$ &
    $\InhId$ \\ \hline
  FInductive tm += &
    1 &
    $[]$ &
    $[]$ &
    $\{"tm" : \TyS{\wcode{\wsig_1}}\}$ &
    $\{"tm" : \TyS{\wcode{\wsig_1'}}\}$ &
    $\InhOv{}{}$ \\ \hline
  | .. | tm\_false &
    2 &
    $["tm" : \cU,$ .. &
    $["tm" : \cU, ..$ &
     &
     &
     \\ \hline
   &
     &
    $"tm_unit"]$ &
    $"tm_unit", "tm_true" ]$ &
     &
     &
     \\ \hline
  FRecursion subst &
     &
     &
     &
     &
     &
     \\ \hline
  (* Inherit ... *) &
    $\alpha$ &
     &
     &
    $\RecSig{\wsig_1}{"tm"}$ &
    $\RecSig{\wsig_1}{"tm"}$ &
    $\InhId$ \\ \hline
  Case tm\_true &
    $\beta$ &
    $\TyTkg{\RecSig{\wsig_1}{"tm"}}$ &
    $\TyTkg{\RecSig{\wsig_1}{"tm"}}$ &
    $\sigma_{\alpha}$ &
    $\{.. "tm:true": \}$ &
    $\InhExt{}{}$ \\ \hline
  End subst &
    3 &
    $A_2$ &
    $A_2'$ &
    $\{.. subst' : \TyLkg{\lsig_\alpha}\}$ &
    $\{.. subst' : \TyLkg{\lsig_\beta'}\}$ &
    $\InhNest{}{}$ \\ \hline
   &
    4 &
    $\TyTkg{\lsig_3}$ &
    $\TyTkg{\lsig_3'}$ &
    $\{.. subst : \El{"tm"} \to \mathbb{N} \to ..\}$ &
    $\{.. subst : \El{"tm"} \to \mathbb{N} \to ..\}$ &
    $\InhOv{}{}$ \\ \hline
  (* Inherit t1 *) &
    5 &
    $["tm":\cU, $ &
    $["tm":\cU, $ &
    $\{.. "t"_1 : \El{"tm"}\}$ &
    $\{.. "t"_1 : \El{"tm"}\}$ &
    $\InhInh{}$ \\ \hline
   &
     &
    $.. subst]$ &
    $.. subst]$ &
     &
     &
     \\ \hline
  \end{tabular}
  \end{table}

>>>>

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{table}[]
  \begin{tabular}{|l|l|l|l|}
  \hline
                          & $i$      & $A_i$             & $A_i'$             \\ \hline
  ***Family STLC\_bool... & 0        &                   &                    \\ \hline
  ***FInductive tm +=     & 1        & $[]$              & $[]$               \\ \hline
                          &          & $["tm" : \cU,$ .. & $["tm" : \cU, ..$  \\
  \multirow{-2}{*}{*** .. | tm\_true | ..} & \multirow{-2}{*}{2} & $"tm_unit"]$                              & $"tm_unit", "tm_true", .. ]$              \\ \hline
  FRecursion subst***     &          &                   &                    \\ \hline
  \rowcolor[HTML]{E0D7D7} 
  (* Inherit ... *)***    & $\alpha$ &                   &                    \\ \hline
  \rowcolor[HTML]{E0D7D7} 
  Case tm\_true***                         & $\beta$             & $\TyTkg{\RecSig{\wsig_1}{"tm"}}$          & $\TyTkg{\RecSig{\wsig_1}{"tm"}}$          \\ \hline
  End subst***            & 3        & $A_2$             & $A_2'$             \\ \hline
                          & 4        & $\TyTkg{\lsig_3}$ & $\TyTkg{\lsig_3'}$ \\ \hline
                                           &                     & $["tm":\cU, .. subst : \El("tm") \to id $ & $["tm":\cU, .. subst : \El("tm") \to id $ \\
  \multirow{-2}{*}{(* Inherit t1 *)***}    & \multirow{-2}{*}{5} & $ \to \El(tm) \to \El(tm) ]$              & $ \to \El(tm) \to \El(tm) ]$              \\ \hline
  \end{tabular}
  \end{table}

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{table}[]
  \begin{tabular}{|l|l|l|l|}
  \hline
   & $i$ & $\sigma_i = \LSigAdd{\sigma_{i-1}}{s_i}{A_i}$ & $\sigma_i' = \LSigAdd{\sigma_{i-1}'}{s_i}{A_i}$ \\ \hline
  ***Family STLC\_bool...                  & 0                   & $\{\}$                                   & $\{\}$                                   \\ \hline
  ***FInductive tm +=                      & 1                   & $\{"tm" : \TyS{\wcode{\wsig_1}}\}$       & $\{"tm" : \TyS{\wcode{\wsig_1'}}\}$      \\ \hline
                                           &                     &                                          &                                          \\
  \multirow{-2}{*}{*** .. | tm\_true | ..} & \multirow{-2}{*}{2} &                                          &                                          \\ \hline
  FRecursion subst***                      &                     &                                          &                                          \\ \hline
  \rowcolor[HTML]{E0D7D7} 
  (* Inherit ... *)***                     & $\alpha$            & $\RecSig{\wsig_1}{"tm"}$                 & $\RecSig{\wsig_1}{"tm"}$                 \\ \hline
  \rowcolor[HTML]{E0D7D7} 
  Case tm\_true***                         & $\beta$             & $\sigma_{\alpha}$                        & $\{.. "tm:true": \}$                     \\ \hline
  End subst***                             & 3                   & $\{.. subst' : \TyLkg{\lsig_\alpha}\}$   & $\{.. subst' : \TyLkg{\lsig_\beta'}\}$   \\ \hline
                                           & 4                   & $\{.. subst : \El{"tm"} \to id \to ..\}$ & $\{.. subst : \El{"tm"} \to id \to ..\}$ \\ \hline
                                           &                     & $\{.. "t"_1 : \El{"tm"}\}$               & $\{.. "t"_1 : \El{"tm"}\}$               \\
  \multirow{-2}{*}{(* Inherit t1 *)***}    & \multirow{-2}{*}{5} &                                          &                                          \\ \hline
  \end{tabular}
  \end{table}

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{table}[]
\begin{tabular}{|l|l|l|}
\hline
                                         & $i$                 & $\goodInh{..}{i_i}{\sigma_i}{\sigma_i'}$             \\ \hline
***Family STLC\_bool...                  & 0                   & $\InhId$                                             \\ \hline
***FInductive tm +=                      & 1                   & $\InhOv{i_1}{\wcode{\wsig_1'}}$                      \\ \hline
                                         &                     &                                                      \\
\multirow{-2}{*}{*** .. | tm\_true | ..} & \multirow{-2}{*}{2} &                                                      \\ \hline
FRecursion subst***                      &                     &                                                      \\ \hline
\rowcolor[HTML]{E0D7D7} 
(* Inherit ... *)***                     & $\alpha$            & $\InhId$                                             \\ \hline
\rowcolor[HTML]{E0D7D7} 
Case tm\_true***                         & $\beta$             & $\InhExt{i_\alpha}{..}$                              \\ \hline
End subst***                             & 3                   & $\InhNest{i_2}{i_\beta}$ with $\uparrow s_3$         \\ \hline
                                         & 4                   & $\InhOv{i_3}{\lambda t. \Wrec{\wsig_1'}{t}{subst'}}$ \\ \hline
                                         &                     & $\InhInh{i_4}$ with $\uparrow s_4$                   \\
\multirow{-2}{*}{(* Inherit t1 *)***}    & \multirow{-2}{*}{5} &                                                      \\ \hline
\end{tabular}
\end{table}
